Results

### 2023-04-05 06_Paper/ER-ED/ERED_Stage2/Manuscript_ERED_Stage2.Rmd
knitted document
corrected BFs in abstract

      - Conceptuatlization

@@

 SVs significantly predicted later choice for an ER strategy ($\chi^2(4, \textit{n} = 119)=115.40$, $p<.001$, $BF10=1.62*1021$).

@@

The authors declare no competing interests.

```{=tex}
\newpage
\setcounter{figure}{0}
```

```{r child = "Figures.Rmd"}
```

# Design Table {#DesignTable}

>>>>

@@

 SVs significantly predicted later choice for an ER strategy ($\chi^2(4, \textit{n} = 119)=115.40$, $p<.001$, $\mathrm{BF}_{\textrm{10}} = 1.62   \times 10^{21}$).

@@

The authors declare no competing interests.
<!--
```{=tex}
\newpage
\setcounter{figure}{0}
```

```{r child = "Figures.Rmd"}
```
-->
# Design Table {#DesignTable}
